Memory Safety: A Systematic Literature Review

### 2024-03-14 paper.tex
First draft of RQ

Before we start researching we must first confirm the need for a SLR. The recent report released by
ONCD~\cite{United_States_Gov2024-pp} has conveniently done this job for us by compiling a report
detailing the need for research in the domain of memory safety. Thus, we must first define the most
important aspect of the planning phase, the research questions.

\subsubsection{Research Questions}

>>>>

Before we start researching we must first confirm the need for a SLR. The recent report released by
ONCD~\cite{United_States_Gov2024-pp} has conveniently done this job for us by compiling a report
detailing the need for research in the domain of memory safety. While the ONCD report detailed a two
pronged approach for this SLR we will be focusing on a memory safe programming language,
specifically Rust.

\subsubsection{Research Questions}
We have defined the following research questions to drive this study.
